%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt]{article} % Font size, can be: 10pt, 11pt or 12pt

\input{structure.tex} % Include the file that specifies the document structure

\renewcommand{\baselinestretch}{1.2}
% Headers and footers can be added with the \lhead{} \rhead{} \lfoot{} \rfoot{} commands
% Example right footer:
%\rfoot{\color{headings}{\sffamily Last update: \today. Typeset with Xe\LaTeX}}

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME
%----------------------------------------------------------------------------------------

\parbox[top][0.12\textheight][c]{\linewidth}{ % Parbox to hold the author name and CV text; fixed height to match the coloured box to the right, centred vertically and full line width
	\vspace{-0.04\textheight} % Reduce whitespace above the parbox to separate it from the main content
	{\color{name}\Huge NOZOMI KAWAMOTO}\\\medskip % Your name
}

\begin{paracol}{2} % Begin the multi-column environment

%----------------------------------------------------------------------------------------
%   CONTACT
%----------------------------------------------------------------------------------------

{\faPhone} \hspace{1mm} +81-80-5755-6326 \\ % Phone number
{\small\faEnvelope} \hspace{1mm} \href{mailto:n0z0me.2ca@gmail.com}{\small n0z0me.2ca@gmail.com} \\ % Email address

\vspace{1cm}

%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------

\section{\Large Education}
\textbf{\color{subtitle}\large Shinshu University}\\
B.S. Engineering(Mar 2019)\\
\\
Main area:\\
Computer Science\\
\\
Research Title:\\
Method for classification of SEP relative to finger vibrotactile stimuli\\

\vspace{1cm}

%----------------------------------------------------------------------------------------
%   SKILLS
%----------------------------------------------------------------------------------------

\section{\Large Skills}
$\cdot$ AWS, GCP, Azure.\\
$\cdot$ Serverless Framework, Ansible.\\
$\cdot$ Python, Javascript, C, etc.\\
$\cdot$ Elastic Stack.\\
$\cdot$ Docker, Kubernetes.\\
$\cdot$ React, Next.js, HTML, CSS.\\
$\cdot$ Git, GitHub.\\

\switchcolumn % Switch to the next paracol column

%----------------------------------------------------------------------------------------
%   PROFILE
%----------------------------------------------------------------------------------------

\section{Profile}
I am Nozomi Kawamoto. I graduated from the faculty of Engineering in Shinshu University, majored in Computer Science. 
My main research was BMI(Brain-Machine Interface) using EEG(Electroencephalogram), and I am better at software engineering than hardware engineering.
About software engineering, my expertise ranges from HTML/CSS/Javascript to low-level programming. And I have solid knowledge on cloud architecture and ETL processing pipeline. 

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%   EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}
\textbf{\color{subtitle}SoftBank} \hspace{0.5mm} {\color{subtitle} - April, 2019 - Present}\\
Full Stack Engineer. Responsible for designing and reliability engineering the distributed search system 
for configuration management for maintaining computer systems, servers, and network switches. 
Also, the search system is used to collect, analyze, and visualize bigdata like a number of server logs.\\

\textbf{\color{subtitle}CiNet} \hspace{0.5mm} {\color{subtitle} - June, 2018 - March, 2019}\\
Research Trainee. Main area was EEG-BMI.\\

\textbf{\color{subtitle}SoftBank} \hspace{0.5mm} {\color{subtitle} - August, 2017}\\
Summer Internship. Responsible for planning some new products and developing these mocks. 
And, functional testing of a whitebox switch.\\

\textbf{\color{subtitle}freee} \hspace{0.5mm} {\color{subtitle} - September, 2017}\\
Summer Internship. SRE Engineer. \\

\textbf{\color{subtitle}Colt Technology} \hspace{0.5mm} {\color{subtitle} - August, 2015}\\
Summer Internship. Network Engineer. Responsible for managing servers and network hardwares in a data center.\\


\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%   LINKS
%----------------------------------------------------------------------------------------

\section{Links}
{\faGithub} \hspace{1mm} \href{https://github.com/n0z0me}{https://github.com/n0z0me}\\ % GitHub profile
{\faLinkedinSquare} \hspace{1mm} \href{https://www.linkedin.com/in/n0z0me/}{https://www.linkedin.com/in/n0z0me/}\\ % LinkedIn profile
{\small\faDesktop} \hspace{0.8mm} \href{https://n0z0me.com}{https://n0z0me.com}\\ % Website
{\faTwitterSquare} \hspace{1mm} \href{https://twitter.com/\_n0z0me}{https://twitter.com/\_n0z0me}\\

\end{paracol}

%----------------------------------------------------------------------------------------

\end{document}
}
